---
title: "p8105_hw6_jc6422"
author: "Jianing Chen"
date: "2024-11-19"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

## Problem 1

Import dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Define bootstrap resampling function

```{r}
set.seed(123)
boot_samples = map(1:5000, ~sample_n(weather_df, size = nrow(weather_df), replace = TRUE))
```

Perform linear regression on each bootstrap sample

```{r}
boot_results = map_dfr(
  boot_samples,
  ~ {
    model = lm(tmax ~ tmin, data = .x)
    glance_result = broom::glance(model) %>% 
      select(r.squared)
    coef_result = broom::tidy(model) %>%
      filter(term != "(Intercept)") %>%
      summarize(log_coef = log(estimate[1] * coef(model)[1]))
    cbind(glance_result, coef_result)
  }
)
```

Compute 2.5% and 97.5% quantiles

```{r}
quantiles = quantile(boot_results$r.squared, probs = c(0.025, 0.975))
quantiles
```

```{r}
logcoef_quantiles = quantile(boot_results$log_coef, probs = c(0.025, 0.975))
logcoef_quantiles
```

Plot the distributions

```{r}
boot_results %>%
  ggplot(aes(x = r.squared)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Bootstrap Distribution of R-Squared", x = "R-Squared", y = "Density")
```

This plot shows the distribution of R^2, which is approximately normal. The range is narrow.

```{r}
boot_results %>%
  ggplot(aes(x = log_coef)) +
  geom_density(fill = "yellow", alpha = 0.5) +
  labs(title = "Bootstrap Distribution of log(beta0 * beta1)", x = "log(beta0 * beta1)", y = "Density")
```

This plot shows the distribution of log(beta0 * beta1), which is also approximately normal. 

## Problem 2

Import dataset

```{r}
data1= read_csv("data/homicide-data.csv")
```
Clean data

```{r}
data1 = data1 %>%
  mutate(
    city_state = paste(city, state, sep = ", "),
    victim_age = as.numeric(victim_age)
  ) %>%
  filter(
    !(is.na(victim_age)),
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  )
data1
```

Fit a Logistic regression for Baltimore,MD

```{r}
balti = data1 %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(resolved = ifelse(disposition == "Closed by arrest", 1, 0))

balti_model = glm(resolved ~ victim_age + victim_sex + victim_race, 
                       family = binomial, data = balti)

balti_model
```

Obtain the estimate and confidence interval of the adjusted odds ratio.

```{r}
balti_or = broom::tidy(balti_model, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term == "victim_sexMale")
balti_or
```

Fit a logistic regression for all cities

```{r}
city = data1 %>%
  mutate(resolved = ifelse(disposition == "Closed by arrest", 1, 0))

city_model = city %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(
    model = map(data, ~ glm(resolved ~ victim_age + victim_sex + victim_race, 
                            family = binomial, data = .x)),
    results = map(model, ~ broom::tidy(.x, conf.int = TRUE, exponentiate = TRUE))
  ) %>%
  unnest(results) %>%
  filter(term == "victim_sexMale") %>%
  select(city_state, estimate, conf.low, conf.high)

city_model
```

Create a plot shows the estimated ORs and CIs for each city.

```{r}
city_model %>%
  ggplot(aes(x = estimate, y = reorder(city_state, estimate))) +
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.6) +
  labs(
    title = "Adjusted Odds Ratios for Male vs Female Victims by City",
    x = "Odds Ratio (Male vs Female)",
    y = "City"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5)
  )

```

Based on this plot, Albuquerque, NM has the largest confidence interval, which suggests a high level of uncertainty, and New York, NY has the smallest confidence interval. 

The majority of cities have adjusted odds ratios close to 1, indicates that there is no significant difference in the likelihood of solving homicides between male and female victims and gender does not play a strong role in determining whether a homicide is resolved.

A few cities show ORs below 1, suggests that homicides involving female victims are resolved at a slightly higher rate. For some cities show ORs higher than 1 indicates a higher likelihood of solving homicides for male victims compared to female victims, but the higher confidence interval reduces the reliability of the observed effect.

## Question 3

Import data

```{r}
data2= read_csv("data/birthweight.csv")
```

Clean the data

```{r}
data2 = data2 %>%
  mutate(
    babysex = factor(babysex, labels = c("Male", "Female")),
    malform = factor(malform, labels = c("Absent", "Present")),
    mrace = factor(mrace),
    frace = factor(frace)
  )
```

Model 1: Hypothesis model

Predictors: `blength`, `gaweeks`, `delwt`, `fincome`, `smoken`,`wtgain`.

```{r}
model1 = lm(bwt ~ blength + gaweeks + delwt + fincome + smoken + wtgain, data = data2)

model1
```

Model 2(simple model): using length at birth and gestational age as predictors

```{r}
model2 = lm(bwt ~ blength + gaweeks, data = data2)
model2
```

Model3(Interaction model): using head circumferenc, length, sex, and all interactions between these

```{r}
model3 = lm(bwt ~ bhead * blength * babysex, data = data2)
model3
```

Add predictions and residuals for model 1

```{r}
data2 = data2 %>%
  add_predictions(model1, var = "pred_bwt") %>%
  add_residuals(model1, var = "resid_bwt")
```

Plot the residuals against fitted values

```{r}
ggplot(data2, aes(x = pred_bwt, y = resid_bwt)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "yellow") +
  labs(
    title = "Residuals vs Fitted Values for Model 1",
    x = "Fitted Values (Predicted Birthweight)",
    y = "Residuals"
  ) +
  theme_minimal()
```




