---
title: "p8105_hw6_jc6422"
author: "Jianing Chen"
date: "2024-11-19"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

Import dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Define bootstrap resampling function

```{r}
set.seed(123)
boot_samples = map(1:5000, ~sample_n(weather_df, size = nrow(weather_df), replace = TRUE))
```

Perform linear regression on each bootstrap sample

```{r}
boot_results = map_dfr(
  boot_samples,
  ~ {
    model = lm(tmax ~ tmin, data = .x)
    glance_result = broom::glance(model) %>% 
      select(r.squared)
    coef_result = broom::tidy(model) %>%
      filter(term != "(Intercept)") %>%
      summarize(log_coef = log(estimate[1] * coef(model)[1]))
    cbind(glance_result, coef_result)
  }
)
```

Compute 2.5% and 97.5% quantiles

```{r}
quantiles = quantile(boot_results$r.squared, probs = c(0.025, 0.975))
quantiles
```

```{r}
logcoef_quantiles = quantile(boot_results$log_coef, probs = c(0.025, 0.975))
logcoef_quantiles
```

Plot the distributions

```{r}
boot_results %>%
  ggplot(aes(x = r.squared)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Bootstrap Distribution of R-Squared", x = "R-Squared", y = "Density")
```

This plot shows the distribution of R^2, which is approximately normal. The range is narrow.

```{r}
boot_results %>%
  ggplot(aes(x = log_coef)) +
  geom_density(fill = "yellow", alpha = 0.5) +
  labs(title = "Bootstrap Distribution of log(beta0 * beta1)", x = "log(beta0 * beta1)", y = "Density")
```

This plot shows the distribution of log(beta0 * beta1), which is also approximately normal. 

## Problem 2

Import dataset

```{r}
data1= read_csv("homicide-data.csv")
```
Clean data

```{r}
data1 = data1 %>%
  mutate(
    city_state = paste(city, state, sep = ", "),
    victim_age = as.numeric(victim_age)
  ) %>%
  filter(
    !(is.na(victim_age)),
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  )
data1
```

Fit a Logistic regression for Baltimore,MD

```{r}
balti = data1 %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(resolved = ifelse(disposition == "Closed by arrest", 1, 0))

balti_model = glm(resolved ~ victim_age + victim_sex + victim_race, 
                       family = binomial, data = balti)

balti_model
```

Obtain the estimate and confidence interval of the adjusted odds ratio.

```{r}
balti_or = broom::tidy(balti_model, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term == "victim_sexMale")
balti_or
```
